\section{Project Plan}
One of the very first tasks I set for myself upon beginning work on this project was to devise a project plan to assist with time management. I wanted to make note of all the official deadlines for the project as well as creating a few unofficial ones to encourage myself to work at an appropriate pace.

\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\textbf{Description} & \textbf{Date} \\ \hline
		Initial Document & 24/10/16 \\ \hline
		Gregynog Presentation & 28-29/11/16 \\ \hline
		\begin{tabular}[c]{@{}c@{}}Gain Understanding of Each Chosen\\ Dynamic Programming Problem\end{tabular} & Before Term 2 Begins \\ \hline
		Project Logs & 27/02/17 \\ \hline
		\begin{tabular}[c]{@{}c@{}}Minimal Implementation\\ of Problems in Java code\end{tabular} & Before March \\ \hline
		Completed Code with Extra Features & Before Easter Break \\ \hline
		Dissertation & 8/05/17 \\ \hline
		Project Fair & 11/05/17 \\ \hline
	\end{tabular}
	\caption{Project Plan - Deadlines}
\end{table}

Similarly I made a weekly timetable to accommodate not just the project but other university work as well to carefully plan out the number of hours I had available to work on different parts of the university course. I updated the table for the second term as well. I aimed for a minimum of 10 hours work on the project each week and kept weekends mostly free to accomodate for any deviations from the timetable on weekdays, allowing for catch-up any work hours missed. For the first term I split the project work into two parts. On Wednesday I would research into the topic of dynamic programming, mainly looking at the theory and making myself notes. On Friday I would look into how I would go about implementing the dynamic programming problems into code, I would begin writing the code properly later in the term, starting with the simpler problems out of the group I had selected.
\smallbreak
Over Christmas break I aimed to dedicate roughly an hour per day to working on the project, but I didn't strictly timetable myself due to the revision for exams and module coursework that was happening around this time. Mostly I worked on the programming portion of the project and managed to make some good progress in these few weeks though. In term 2 I kept my aim of 5 hours per week spent on project work, split between Thursday and Friday. On Thursday I would continue documenting the problems and later when I felt I had achieved enough, I spent time testing code and beginning to write the dissertation towards the latter weeks of the term. On Friday I continued programming the problems in Java, I managed to build up a lot of speed compared to my progress in the first term and got every program working by the time Easter break began, with only minor updates needed from thereon. Finally, over the Easter break, my main focus was on writing this dissertation as well as tying up any loose ends, including planning for the project fair.

\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		\textbf{Day} & \textbf{Term 2} & \textbf{Term 2} \\ \hline
		Monday & \begin{tabular}[c]{@{}c@{}}3 Hours - Lectures\\ 2 Hours - Module Work\end{tabular} & \begin{tabular}[c]{@{}c@{}}4 Hours - Lectures\\ 3 Hours - Module Work\end{tabular} \\ \hline
		Tuesday & \begin{tabular}[c]{@{}c@{}}3 Hours - Lectures\\ 2 Hours - Module Work\end{tabular} & \begin{tabular}[c]{@{}c@{}}4 Hours - Lectures\\ 2 Hours - Module Work\end{tabular} \\ \hline
		Wednesday & \begin{tabular}[c]{@{}c@{}}5 Hours Project Work\\ Researching the Topic\end{tabular} & \begin{tabular}[c]{@{}c@{}}5 Hours - Project Work\\ Documenting Problems\end{tabular} \\ \hline
		Thursday & \begin{tabular}[c]{@{}c@{}}3 hours - Lectures\\ 2 Hours - Module Work\end{tabular} & \begin{tabular}[c]{@{}c@{}}5 Hours - Project Work\\ Coding / Implementation\end{tabular} \\ \hline
		Friday & \begin{tabular}[c]{@{}c@{}}5 Hours Project Work\\ Looking Into Implementation\end{tabular} & \begin{tabular}[c]{@{}c@{}}3 Hours - Lectures\\ 2 Hours - Module Work\end{tabular} \\ \hline
		Weekend & \begin{tabular}[c]{@{}c@{}}Reserve 4 Hours Each Day\\ For Any Work Which Overflows\end{tabular} & \begin{tabular}[c]{@{}c@{}}Reserve 4 Hours Each Day\\ For Any Work Which Overflows\end{tabular} \\ \hline
	\end{tabular}
	\caption{Project Plan - Weekly Timetable}
\end{table}